Paper Analysis

### 2024-10-21 Paper_WriteUp/Paper_Plots.qmd
tidying

bullet_data |> nrow()

## average number, we remove the two accounts with 1 and 3 games only
## throughout we do not consider those who play less than 10 games
## at a given format when fitting any model
bullet_data |> 
  group_by(Username) |> 
  count() |> 
  filter(n > 3) |>
  ungroup() |> 
  summarise(avg = mean(n))

>>>>

bullet_data |> nrow()
## average number, we remove the two accounts with 1 and 3 games only
## throughout we do not consider those who play less than 10 games
## at a given format when fitting any model
bullet_data |> 
  group_by(Username) |> 
  count() |> 
  filter(n > 3) |>
  ungroup() |> 
  summarise(avg = mean(n))
